---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# econdata

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Curated datasets used in influential empirical macroeconomics papers, with a
catalog of categories and tags, pointers to external replication data, and CSV
copies served from the package website so you can use them from any language.

## Installation

``` r
# install.packages("pak")
pak::pak("kvasilopoulos/econdata")
```

## Usage

Each dataset is an object named after the paper it comes from:

```{r}
library(econdata)

sw2001 # Stock and Watson (2001)
```

The `catalog` lists everything with categories, tags and sample ranges:

```{r}
catalog[, c("key", "category", "frequency", "start", "end", "nrow", "ncol")]

# Datasets tagged "var"
catalog$key[sapply(strsplit(catalog$tags, "|", fixed = TRUE), function(t) "var" %in% t)]
```

## Static CSV API

Every dataset is also published as CSV at
`https://kvasilopoulos.github.io/econdata/data/<key>.csv`, with a JSON index at
[`data/index.json`](https://kvasilopoulos.github.io/econdata/data/index.json).
No R required:

``` r
read.csv("https://kvasilopoulos.github.io/econdata/data/sw2001.csv")
```

``` python
pd.read_csv("https://kvasilopoulos.github.io/econdata/data/gk2015.csv", parse_dates=["date"])
```

## Finding other replication data

`sources` (and the [site](https://kvasilopoulos.github.io/econdata/#finding-other-replication-data))
lists freely available datasets behind commonly replicated papers:
FRED-MD, Kilian's oil data, Shiller's stock data, the Macrohistory database,
uncertainty and shadow-rate series and more.

```{r}
sources[grepl("monetary-policy", sources$tags), c("name", "coverage")]
```

Column definitions for the wide panels (`bbe2005`, `r2016_*`, `rz2018`):

```{r}
subset(variables, dataset == "rz2018")[1:5, ]
```

## Datasets

```{r echo = FALSE}
knitr::kable(catalog[, c("key", "title", "category", "frequency")])
```

Replication notebooks: [Stock and Watson (2001)](https://kvasilopoulos.github.io/econdata/articles/replication-sw2001.html),
[Bernanke, Boivin and Eliasz (2005)](https://kvasilopoulos.github.io/econdata/articles/replication-bbe2005.html).

## Contributing

* Add a dataset: put the raw file under `data-raw/<key>/`, add a block to
  `data-raw/DATASETS.R`, a bib entry to `data-raw/bib/papers.bib`, and a row
  to `data-raw/catalog.csv`. Then run `data-raw/bib/create_papers.R`,
  `data-raw/catalog.R` and `data-raw/site.R` (rebuilds `docs/`).
* Add an external source: a row in `data-raw/sources.csv`.
* We follow the [tidyverse principles](.github/CONTRIBUTING.md); see also
  [PKG_CONTRIBUTING.md](.github/PKG_CONTRIBUTING.md).

Please note that the 'econdata' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
