---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# econdata

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/econdata)](https://CRAN.R-project.org/package=econdata)
<!-- badges: end -->

In Economics authors have collected their own research data or used external datasets. The goal of {econodata} is to provide a curated list of datasets that are used in the most influential economic papers. 

## Installation

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/econdata")
```

# Usage

All data are stored as objects in unquoted name format.

```{r}
library(econdata)

# Stock and Watson (2001) dataset
sw2001
```

# Papers

```{r include=FALSE}
library(knitr)
library(kableExtra)
# library(DT)
```

```{r echo=FALSE}
papers[,1:3] %>% 
  # DT::datatable()
  kable() %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "20em")
```

### Contributing to the Package

If you want to contribute to the package:

* We follow the [tidyverse principles](.github/CONTRIBUTING.md)
* Specific instructions to contribute to the package can be found [here](.github/PKG_CONTRIBUTING.md).

---

Please note that the 'econdata' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

