---
title: "Dataset catalog"
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(econdata)
base <- "https://kvasilopoulos.github.io/econdata/data/"
link <- function(text, href) sprintf('<a href="%s">%s</a>', href, text)
```

Every dataset in the package is also published as a plain CSV, so you can use
it from any language without installing the package:

```r
# R
sw2001 <- read.csv("https://kvasilopoulos.github.io/econdata/data/sw2001.csv")

# Python
import pandas as pd
sw2001 = pd.read_csv("https://kvasilopoulos.github.io/econdata/data/sw2001.csv", parse_dates=["date"])

# Stata
import delimited "https://kvasilopoulos.github.io/econdata/data/sw2001.csv", clear
```

Machine-readable index: [`data/index.json`](`r paste0(base, "index.json")`)
(same fields as this table, with tags as arrays), [`data/catalog.csv`](`r paste0(base, "catalog.csv")`),
[`data/papers.csv`](`r paste0(base, "papers.csv")`) and the [`data/papers.bib`](`r paste0(base, "papers.bib")`)
bibliography.

## Datasets

Type in the search box to filter by tag, category or variable name.

```{r}
tbl <- catalog
tbl$key <- link(tbl$key, paste0("../reference/", tbl$key, ".html"))
tbl$csv <- link("csv", paste0(base, catalog$key, ".csv"))
tbl$paper <- ifelse(is.na(tbl$paper), "",
  link(papers$AUTHORYEAR[match(tbl$paper, papers$BIBTEXKEY)], tbl$source_url))
tbl$sample <- paste(format(tbl$start, "%Y-%m"), "to", format(tbl$end, "%Y-%m"))
tbl$dim <- paste(tbl$nrow, "x", tbl$ncol)
tbl$tags <- gsub("|", " ", tbl$tags, fixed = TRUE)
tbl <- tbl[c("key", "csv", "title", "paper", "category", "tags", "frequency", "sample", "dim", "variables")]
DT::datatable(tbl, escape = FALSE, rownames = FALSE, filter = "top",
              options = list(pageLength = 25, dom = "ft", scrollX = TRUE,
                             columnDefs = list(list(targets = 9, visible = FALSE))))
```

Column definitions for the 120-series panel in `bbe2005` are in
[`data/bbe2005-variables.csv`](`r paste0(base, "bbe2005-variables.csv")`).

## Tags

```{r results = "asis"}
tags <- sort(table(unlist(strsplit(catalog$tags, "|", fixed = TRUE))), decreasing = TRUE)
cat(paste0("`", names(tags), "` (", tags, ")", collapse = ", "))
```
