---
title: "Finding replication data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, results = "asis")
library(econdata)
```

The datasets bundled in `econdata` are small, frozen snapshots. Most
empirical macro papers rely on a handful of series that are maintained and
updated by their authors or by a central bank. This page lists those sources,
which papers use them, and where to download them. The same table is available
as [`data/sources.csv`](https://kvasilopoulos.github.io/econdata/data/sources.csv)
and as the `sources` object in the package.

A few general rules that save time when reproducing a paper:

* **AEA journals** (AER, AEJ, JEP, P&P) since 2019 require a replication
  package on openICPSR; search by DOI. Older AEA papers usually have a
  "Data Set" zip on the article page.
* **Top-5 journals** (QJE, JPE, Econometrica, ReStud) deposit on Harvard
  Dataverse; search by title.
* **Author websites** are still the best source for shock series (Ramey,
  Mertens, Jarocinski, Bauer, Miranda-Agrippino, Ludvigson) because the
  authors keep extending them past the published sample.
* **FRED-MD/QD** reproduces almost any US large-panel exercise (factor
  models, FAVARs) and ships monthly vintages, so pin the vintage you used.

```{r}
by_cat <- split(sources, factor(sources$category, unique(sources$category)))
for (cat_name in names(by_cat)) {
  s <- by_cat[[cat_name]]
  cat("\n## ", cat_name, "\n\n")
  for (i in seq_len(nrow(s))) {
    cat(sprintf("**[%s](%s)** &mdash; %s  \n", s$name[i], s$url[i], s$notes[i]))
    cat(sprintf("<small>Used in: %s. Frequency: %s. Coverage: %s. Tags: %s.</small>\n\n",
                s$used_in[i], s$frequency[i], s$coverage[i],
                gsub("|", ", ", s$tags[i], fixed = TRUE)))
  }
}
```

## Missing something?

Open an [issue](https://github.com/kvasilopoulos/econdata/issues) with the
paper, the URL and a line on what the data are, or edit
[`data-raw/sources.csv`](https://github.com/kvasilopoulos/econdata/blob/master/data-raw/sources.csv)
and send a pull request.
